Actuator line modeling of vertical-axis turbines

### 2016-04-29 paper.tex
Mention validation against two turbines in the intro

It is therefore proposed that an actuator line model may be the optimal
combination of high-fidelity flow modeling that includes performance
predictions, but with reduced computational expense. Here we will develop and
evaluate the effectiveness of an ALM for cross-flow turbines inside both RANS
and LES simulations, implemented as an extension for the OpenFOAM open-source
CFD library.

>>>>

It is therefore proposed that an actuator line model may be the optimal
combination of high-fidelity flow modeling that includes performance
predictions, but with reduced computational expense. Here we have developed an
ALM for cross-flow turbines inside both RANS and LES simulations, implemented as
an extension for the OpenFOAM open-source CFD library. This model was validated
against experimental data for both a high \cite{Bachant2015-JoT} and a medium
\cite{Bachant2016-RM2-paper} solidity vertical-axis turbine.
